Figure 6. Differential Protein expression

### 2023-03-08 reports/manuscript/Figure6.Rmd
reorder cytokine plot for proof

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(readxl)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
Protein_V3 <- read_xlsx("../../data/Protein_norm_MFI_Bradley_et.al.xlsx")
cytokine_data <- read.csv("../../data/210125_Cytokines_visit3CVL.csv")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)

#################
# COLOR PALETTS #
#################
pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
```

```{r DPE Functions, message=FALSE, warning=FALSE, include=FALSE}
################################
# DEG's FUNCTION ACROSS GROUPS #
################################
#group <- "Tissue_gr"
#group <- "Luminal_gr"
#group <- "L_T_groups"
limma_dpe.fun <- function(group, confound) {
  groups <- metadata[sample_use, group]
  n_gr <- length(na.omit(unique(groups)))

@@

```{r format data, echo=FALSE, warning=FALSE, message=FALSE}
to_remove <- c("CSTB_HPA017380","SPINK5_HPA009067","SPRR3_HPA024330","FGA_HPA064755","S100A12_HPA002881","KRT1_HPA019797","KRT1_HPA062908","LGMN_HPA001426","TACSTD2_HPA043104","FLNA_HPA001115","GPX3_HPA071520","CSTA_HPA001031","SERPINB5_HPA019132","ITIH2_HPA059150","NCF2_HPA002327","ANXA3_HPA013431")

@@

```{r Across and Pairwise tables, include=FALSE}
# Samples to use
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
sample_use <- intersect(metadata$ID, colnames(TRX)[colSums(TRX)!=0])
sample_use <- intersect(colnames(Protein), sample_use)

@@

```{r heatmap functions, echo=FALSE}
top_dpe.fun <- function(top){
  p_val <- pull(top, "P.Value")
  top_dpe <- (p_val < 0.05) #& (rowSums( abs(top[,grep("logFC",colnames(top))]) >= log2(1.5) ) >= 1)
  top_dpe <- top$Antibody[ top_dpe ]

@@

  if(layout == "multi") {
    layout(matrix(c(1,2,5,6,
                    7,7,8,8,
                    3,3,4,4),
           nrow = 3, ncol = 4,byrow = T),
           widths = c(1,2,.8,2), heights = c(1,1,.01) ) }
  if(layout == "single") {
    layout(matrix(c(1,2),
                    nrow = 1, ncol = 2,byrow = T),widths = c(1,2) ) }

    ## Dendogram
    par(mgp=c(0,0.2,0), mar=c(4,.6,2.5,.2)) #(bottom, left, top, right) 
    plot( rev(as.dendrogram(h)) , xlim=c(max(h$height),-.01),
          horiz = T, leaflab = "none",xaxs="i",yaxs="i",axes=T, cex.axis = .7 )
    #title(xlab="height", line=3)
    mtext( c("Height"), side=1, las = 1, cex = .7, line =1,xpd=T)

    if(gr == "Tissue_gr") {
      height <-1.5 
      add_letter("c")
    }else{
      add_scale_legend(x = par("usr")[1]-0.1, height = 1.5,#diff(par("usr")[3:4])-20,
                     pal = colorRampPalette(c("navy","grey95","firebrick"))(91),
                     labels = c("-5","0","5"))
      height <- round(max(h$height))
      add_letter("a")}
    #lines(x=c(0,height), y=c(0.45,0.45), col="black", lty=1, lwd = 2.5) # only for grob

    ## Heatmap
    par(mar=c(4,.2,2.5,2.5)) #(bottom, left, top, right) 
    image( t(top_PROT_mfi[h$order,pull(df, "ID")][nrow(top_PROT_mfi):1,]),
           col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
           breaks = breaks,
           axes=F)
    mtext( "Differentialy Expressed Proteins", side=3, las = 1, cex = .7, font = 2, line =1.5,xpd=T)
    mtext( c("Study Groups"), side=1, las = 1, cex = .7, line = 1,xpd=T)

@@

    points( seq(0,1,length.out = ncol(top_PROT_mfi)),rep(par("usr")[3],ncol(top_PROT_mfi))-.008,
            col=c("tomato","orange","#d7d7d7")[ factor(metadata[samples,"BV_Diagnosis_v3"][order(df[1])]) ],
            pch=15,xpd=T,cex=size) 
    points( seq(0,1,length.out = ncol(top_PROT_mfi)),rep(par("usr")[3],ncol(top_PROT_mfi))-.022,
            col= c("#d7d7d7","tomato")[ factor(metadata[samples,"HIVstatus"][order(df[1])]) ],
            pch=15,xpd=T,cex=size)

    mtext( paste0(" ", gsub("_.+","",rownames(top_PROT_mfi)[rev(h$order)])), side=4, las = 1, cex = .45,
           at=seq(0,1,length.out = length(rownames(top_PROT_mfi))), xpd=T)

@@

```{r sig. cytokines function, include=FALSE}
sig_stars.fun <- function(df_krusk, df_dunn, group, n = 6, order = NULL){
  samples_use <- metadata[,c(group, "ID")] %>% na.omit() %>% filter(ID %in% colnames(cytokine_data))

@@

```{r Cytokine stats tests, include=FALSE}
cytokine_data$ID <- metadata [ match( cytokine_data$PatID , as.character(metadata$PatID)  ) ,"ID" ]
cytokine_data <- cytokine_data[ !is.na(cytokine_data$ID) , ]
rownames(cytokine_data) <- cytokine_data$ID
cytokine_data <- cytokine_data[,grepl("CVL",colnames(cytokine_data))]
colnames(cytokine_data) <- sub("CVL_","",colnames(cytokine_data))
cytokine_data <- t(cytokine_data)
cytokine_data[is.na(cytokine_data)] <- 0.01
cytokine_data <- log2(cytokine_data+1)
cytokine_data_log <- cytokine_data

@@

```{r Suppl. Tbl. 15 16 & 17, include=FALSE}
names <- c("15 Luminal", "16 Tissue") %>% set_names()

@@

```{r Figure 6, echo = FALSE, eval = TRUE, fig.height=10, fig.width=7}
figlabels <- letters
####################################
# TOP DIFF. EXPRESSED PROT HEATMAP #
####################################
### A
# Luminal groups
t <- top_dpe.fun(dpe_L$top)
plot_heatmap.fun(t, "Luminal_gr", scale = T, layout = "multi")

@@

##############################
# SIG. CYTOKINES VIOLIN PLOT #
##############################
### B
# Luminal groups
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
stars <- Luminal$stars_df

par( mar=c(1.4,5,1.5,2)) #b,l,t,r 
violist(data=Luminal$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= g, #add_ylims = T, #gives starting value of y-axis and max value of all data points
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings))
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = .9)

@@

### D
# Tissue groups
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
stars <- Tissue$stars_df

par( mar=c(20.4,6,1.5,3)) #b,l,t,r
violist(data=Tissue$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= rownames(Tissue$sig_df), 
          col = pal, transparency = 50, #add_ylims = T,
          clustering=Tissue$groupings )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Tissue gr. Cytokines", line = 0.7, cex.main = .9)

@@

**Figure 6. Protein Heatmap**. **a** and **c** top differentially expressed proteins scaled by row, for Luminal and Tissue respectively. (p-value < 0.05) **b** and **d** sig. cytokines for Luminal and Tissue respectively.

```{r All dpe plot, eval=FALSE, fig.height=6, fig.width=6, include=FALSE}
library(cowplot)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results    = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width  = 6.6929133858,
  fig.align  = "center",
  fig.path   = "./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load-data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(readxl)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

prot_url <- "https://doi.org/10.1371/journal.ppat.1010494.s017"
#cyt_url <- ""
#meta_url <- ""

############
# DOWNLOAD #
############
if(isFALSE(file.exists("../../data/Protein_norm_MFI.xlsx"))){download.file(prot_url, paste0("../../data/", "Protein_norm_MFI.xlsx"), method="auto")}
#if(isFALSE(file.exists("../../data/Cytokine_data.xlsx"))){download.file(cyt_url, paste0("../../data/", "Cytokine_data.xlsx"), method="auto")}
#if(isFALSE(file.exists("../../data/metadata.xlsx"))){download.file(meta_url, paste0("../../data/", "metadata.xlsx"), method="auto")}

#############
# LODA DATA #
#############
# datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
Protein_V3 <- read_xlsx("../../data/Protein_norm_MFI.xlsx", skip = 2) %>% rename(ID="Patient/Sample ID")
# cytokine_data <- read.csv("../../data/210125_Cytokines_visit3CVL.csv")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)

cytokine_data <- read_xlsx(paste0("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/data/", "Cytokine_data.xlsx"), na = "NA", sheet = "Cytokine_data") 
#################
# COLOR PALETTS #
#################
pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
```

```{r DPE-Functions, message=FALSE, warning=FALSE, include=FALSE}
################################
# DEG's FUNCTION ACROSS GROUPS #
################################
#group <- "Tissue_gr"
#group <- "Luminal_gr"
#group <- "L_T_groups"
limma_dpe.fun <- function(group, confound) {
  groups <- metadata[sample_use, group]
  n_gr <- length(na.omit(unique(groups)))

@@

```{r format-data, echo=FALSE, warning=FALSE, message=FALSE}
to_remove <- c("CSTB_HPA017380","SPINK5_HPA009067","SPRR3_HPA024330","FGA_HPA064755","S100A12_HPA002881","KRT1_HPA019797","KRT1_HPA062908","LGMN_HPA001426","TACSTD2_HPA043104","FLNA_HPA001115","GPX3_HPA071520","CSTA_HPA001031","SERPINB5_HPA019132","ITIH2_HPA059150","NCF2_HPA002327","ANXA3_HPA013431")

@@

```{r Across-and-Pairwise-tables, include=FALSE}
# Samples to use
# TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
# sample_use <- intersect(metadata$ID, colnames(TRX)[colSums(TRX)!=0])
sample_use <- metadata$ID
sample_use <- intersect(colnames(Protein), sample_use)

@@

```{r heatmap-functions, echo=FALSE}
top_dpe.fun <- function(top){
  p_val <- pull(top, "P.Value")
  top_dpe <- (p_val < 0.05) #& (rowSums( abs(top[,grep("logFC",colnames(top))]) >= log2(1.5) ) >= 1)
  top_dpe <- top$Antibody[ top_dpe ]

@@

  if(layout == "multi") {
    layout(matrix(c(1,2,5,6,
                    7,7,8,8,
                    7,7,9,9,
                    3,3,4,4),
           nrow = 4, ncol = 4,byrow = T),
           widths = c(1,2,.8,2), heights = c(1,.35,.35,.01) )
    # layout.show(9)
    }
  if(layout == "single") {
    layout(matrix(c(1,2),
                    nrow = 1, ncol = 2,byrow = T),widths = c(1,2) ) }

    ## Dendogram
    par(mgp=c(0,0.2,0), mar=c(4,.6,2.5,.2)) #(bottom, left, top, right) 
    plot( rev(as.dendrogram(h)) , xlim=c(max(h$height),-.01),
          horiz = T, leaflab = "none",xaxs="i",yaxs="i",axes=T, cex.axis = .8 )
    #title(xlab="height", line=3)
    mtext( c("Height"), side=1, las = 1, cex = .7, line =1,xpd=T)

    if(gr == "Tissue_gr") {
      height <-1.5 
      add_letter("c")
    }else{
      # add_scale_legend(x = par("usr")[1]-0.1, height = 1.5,#diff(par("usr")[3:4])-20,
      #                pal = colorRampPalette(c("navy","grey95","firebrick"))(91),
      #                labels = c("-5","0","5"))
      # height <- round(max(h$height))
      # add_letter("a")
      }
    #lines(x=c(0,height), y=c(0.45,0.45), col="black", lty=1, lwd = 2.5) # only for grob

    ## Heatmap
    par(mar=c(4,.2,2.5,3.2)) #(bottom, left, top, right) 
    image( t(top_PROT_mfi[h$order,pull(df, "ID")][nrow(top_PROT_mfi):1,]),
           col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
           breaks = breaks,
           axes=F)
    mtext( "Differentialy Expressed Proteins", side=3, las = 1, cex = .7, font = 2, line =1.5,xpd=T)
    mtext( c("Study Groups"), side=1, las = 1, cex = .7, line = 1,xpd=T)

@@

    points( seq(0,1,length.out = ncol(top_PROT_mfi)),rep(par("usr")[3],ncol(top_PROT_mfi))-.008,
            col=c("tomato","orange","#d7d7d7")[ factor(metadata[samples,"BV_Diagnosis_v3"][order(df[1])]) ],
            pch=15,xpd=T,cex=size) 
    points( seq(0,1,length.out = ncol(top_PROT_mfi)),rep(par("usr")[3],ncol(top_PROT_mfi))-.020,
            col= c("#d7d7d7","tomato")[ factor(metadata[samples,"HIVstatus"][order(df[1])]) ],
            pch=15,xpd=T,cex=size)

    mtext( paste0(" ", gsub("_.+","",rownames(top_PROT_mfi)[rev(h$order)])), side=4, las = 1, cex = .53,
           at=seq(0,1,length.out = length(rownames(top_PROT_mfi))), xpd=T)

@@

```{r sig-cytokines-function, include=FALSE}
sig_stars.fun <- function(df_krusk, df_dunn, group, n = 6, order = NULL){
  samples_use <- metadata[,c(group, "ID")] %>% na.omit() %>% filter(ID %in% colnames(cytokine_data))

@@

```{r Cytokine-stats-tests, include=TRUE}
cytokine_data <- cytokine_data %>% 
  column_to_rownames(var = "ID") %>% 
  as.matrix()

cytokine_data <- t(cytokine_data)
cytokine_data[is.na(cytokine_data)] <- 0.01
cytokine_data <- log2(cytokine_data+1)
cytokine_data_log <- cytokine_data

@@

```{r Suppl. Tbl. 15 16 & 17, include=TRUE, results = 'hide'}
names <- c("15 Luminal", "16 Tissue") %>% set_names()

@@

```{r Figure 6, echo = TRUE, eval = TRUE, fig.height=10, fig.width=7}
# dev.new(height=10, width=6.6929133858, noRStudioGD = TRUE)
figlabels <- letters
####################################
# TOP DIFF. EXPRESSED PROT HEATMAP #
####################################
### A
# Luminal groups
t <- top_dpe.fun(dpe_L$top)
plot_heatmap.fun(t, "Luminal_gr", scale = T, layout = "multi")

@@

##############################
# SIG. CYTOKINES VIOLIN PLOT #
##############################
### B
# Luminal groups
g <- c("MIG", "IL1b", "IL12_p70", "MCP1", "IL1a", "IP10") 
#g <- c("MIG", "IL12_p70","IL1a", "IP10", "IL1b", "MCP1" )
lab <- c("MIG", "IL-1\u03b2", "IL-12-p70", "MCP-1", "IL-1\u03b1", "IP-10" )
#lab <- c("IP-10", "IL-1\u03b2", "IL-12-p70", "MCP-1","IL-1\u03b1", "MIG")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g[1:4])
rownames(Luminal$sig_df) <- lab
stars <- Luminal$stars_df

par( mar=c(1.4,5,1.5,2)) #b,l,t,r 
violist(data=Luminal$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= lab[1:4],
          #cex.axis = 1.1,
          #add_ylims = T, #gives starting value of y-axis and max value of all data points
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings))
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = 1.1)

@@

Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g[5:6])
rownames(Luminal$sig_df) <- lab
stars <- Luminal$stars_df 
par(mar=c(1.4,5,1.5,2) ) #b,l,t,r
violist(data=Luminal$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= lab[5:6],
          #add_ylims = T, #gives starting value of y-axis and max value of all data points
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings))
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_)
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = 1.1)

### D
# Tissue groups
lab <- c("IL-1\u03b1", "IP-10")
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
rownames(Tissue$sig_df) <- lab
stars <- Tissue$stars_df

#par(mar=c(20.4,6,1.5,3)) #b,l,t,r # ps = 20, point size
par(mar=c(1,5,1.5,5)) #b,l,t,r
violist(data=Tissue$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= rownames(Tissue$sig_df),
          col = pal, transparency = 50,
          # add_ylims = T,
          clustering=Tissue$groupings )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_)
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Tissue gr. Cytokines", line = 0.7, cex.main = 1.1)

@@

**Figure 6. Characterization of the host protein profile as stratified by the luminal and tissue-adherent microbiome study groups.** All study samples were assessed for significant differences in protein levels across the study groups. **a**,**b** The five luminal study groups and **c**,**d** the five corresponding tissue groups. a, c Proteins with a p-value > 0.05 were omitted from the heatmap. Proteins with significantly different levels across the groups were clustered by hierarchical agglomerative clustering using inverse Pearson’s correlation as distance measure and Ward’s method (“ward. D2”) for linkage. Color-coded rows below the heatmaps show clinical diagnosis of bacterial vaginosis (BV, binned Nugent’s scores) and HIV diagnosis, respectively. Color coding for BV: Gray: negative, orange: intermediate, red: positive; and for HIV: Gray: HIV seronegative, red: HIV seropositive. b, d Violin plots of log2 transformed cytokine levels across the luminal and tissue study groups (as indicated on the x-axis), respectively. The asterisk and lines indicate statistically significant results of Dunn’s test with Benjamini Hochberg’s correction analysis. Adjusted p-values: * < 0.05, ** < 0.01, *** < 0.001, **** < 0.0001

```{r old-Figure 6, echo = FALSE, eval = FALSE, fig.height=10, fig.width=7}
# old layout
    # layout(matrix(c(1,2,5,6,
    #                 7,7,8,8,
    #                 3,3,4,4),
    #        nrow = 3, ncol = 4,byrow = T),
    #        widths = c(1,2,.8,2), heights = c(1,1,.01) )
figlabels <- letters
####################################
# TOP DIFF. EXPRESSED PROT HEATMAP #
####################################
### A
# Luminal groups
t <- top_dpe.fun(dpe_L$top)
plot_heatmap.fun(t, "Luminal_gr", scale = T, layout = "multi")

##############################
# SIG. CYTOKINES VIOLIN PLOT #
##############################
### B
# Luminal groups
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
lab <- c("IL-1\u03b1", "MIG", "IP-10", "IL-1\u03b2", "IL-12-p70", "MCP-1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
rownames(Luminal$sig_df) <- lab
stars <- Luminal$stars_df

par( mar=c(1.4,5,1.5,2)) #b,l,t,r 
violist(data=Luminal$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= lab,
          #add_ylims = T, #gives starting value of y-axis and max value of all data points
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings))
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = .9)

### D
# Tissue groups
lab <- c("IL-1\u03b1", "IP-10")
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
rownames(Tissue$sig_df) <- lab
stars <- Tissue$stars_df

par(mar=c(20.4,6,1.5,3)) #b,l,t,r # ps = 20, point size
violist(data=Tissue$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= rownames(Tissue$sig_df), 
          col = pal, transparency = 50, 
          # add_ylims = T,
          clustering=Tissue$groupings )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Tissue gr. Cytokines", line = 0.7, cex.main = .9)

```{r All-dpe-plot, eval=FALSE, fig.height=6, fig.width=6, include=FALSE}
library(cowplot)
